Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-22 manuscript.Rmd
establish coordinate reference system

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
load("data/travel_times.RData")
theme_map <- theme_void()

@@

travel_time_sf <- left_join(x = travel_times, y = DC_census, by = c("dest_id" = "id")) %>%
	st_as_sf()
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
load("data/travel_times.RData")
theme_map <- theme_void()

@@

travel_time_sf <- left_join(x = travel_times, y = DC_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```
